TGI-spinal-power

### 2022-05-09 analysis/tgispine_lme_power.Rmd
creating warm and cold zero inflated models

# Getting data and reformatting to fit model
```{r}
df <- read.csv('STGI_compiled-data.csv')

@@

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(cold ~ manipulation + condition + cold_location + (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df)
summary(model.cold)
# then model warm VAS
```
# Look at model assumptions
```{r}
model.cold.assmup <- simulateResiduals(model.cold)
plot(model.cold.assmup)
```

# View the coefficients for each person (should vary, due to random slope model)

>>>>

# Getting data and reformatting to fit model
```{r}
# import compiled data
df <- read.csv('STGI_compiled-data.csv')

@@

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'cold' ,])
# then model warm VAS
model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'warm' ,])
# model summaries
summary(model.cold)
summary(model.warm)
```
# Look at model assumptions
```{r}
# cold assumption
model.cold.assmup <- simulateResiduals(model.cold)
plot(model.cold.assmup)
```

```{r}
# warm assumption
model.warm.assump <- simulateResiduals(model.warm)
plot(model.warm.assump)
```
